Consistency scores in text data

### 2020-07-14 outputs/documents/paper.Rmd
n-gram statistic principal notations

[Statistic notation of n-gram?]

[Character-level n-gram?]

>>>>

The probability of a sequence appearing in a corpus follows the chain rules:

> P(We,had,been,wandering) $=$ P(We)$\cdot$P(had|We)$\cdot$P(been|We,had)$\cdot$P(wandering|We,had,been)

This will soon grow weary if the sentences are long. Instead, the Markov assumption permits us to approximate the probability using only the last $n$ words. More specifically:

> P(We,had,been,wandering)$\approx$ P(We)$\cdot$P(had|We)$\cdot$P(been|had)$\cdot$P(wandering|been)

Simplified and formalized to:

> P($w^{n}_{1}) \approx$ P($w_{1}$) $\cdot$ P($w_{2} | w_{1}$) ... P($w_{n} | w_{n-1}$)
